Reproducibility of SNP calling in multiple sequencing runs from single tumors

### 2014-06-01 PAPER/rough_draft.tex
added title and moved figures to the end

\title{Needs a title...}
\author{Dakota Z. Derryberry, Claus O. Wilke, Matthew C. Cowperthwaite}

@@

\begin{figure}
\includegraphics[scale=0.5]{C282_v_C484.png}
\caption{This figure plots the number of putative SNPs called by SomaticSniper (unfiltered) using the WGS v. WGA. Each point is a patient. The line is y=x, so points falling below the line agree with the hypothesis that whole genome amplification makes more mutations in a sample.}
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{unfiltered_overlap_WGS_WGA_together_densities.png}
\caption{This figure shows the density of the percentage of each WGS (blue) and WGA (red) sample that overlaps with the other sample from the same patient. The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter. }
\end{figure}

@@

\begin{figure}
\includegraphics[scale=0.5]{unfiltered_total_muts_v_percent_overlap.png}
\caption{Plot of the percentage of the WGA samples that overlaped with the corresponding WGS samples (as a measure of sample quality) against the total number of putative SNPs in the WGS sample}
\end{figure}

@@

>>>>

\title{Reproducibility of SNP calling in multiple sequencing runs from single tumors}
\author{Dakota Z. Derryberry, Claus O. Wilke, Matthew C. Cowperthwaite}

@@

@@

@@

@@

\section{Figures}

\begin{figure}
\includegraphics[scale=1.0]{C282_v_C484.png}
\caption{This figure plots the number of putative SNPs called by SomaticSniper (unfiltered) using the WGS v. WGA. Each point is a patient. The line is y=x, so points falling below the line agree with the hypothesis that whole genome amplification makes more mutations in a sample.}
\end{figure}

\begin{figure}
\includegraphics[scale=1.0]{unfiltered_overlap_WGS_WGA_together_densities.png}
\caption{This figure shows the density of the percentage of each WGS (blue) and WGA (red) sample that overlaps with the other sample from the same patient. The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter. }
\end{figure}

\begin{figure}
\includegraphics[scale=1.0]{unfiltered_total_muts_v_percent_overlap.png}
\caption{Plot of the percentage of the WGA samples that overlaped with the corresponding WGS samples (as a measure of sample quality) against the total number of putative SNPs in the WGS sample}
\end{figure}
